---
title: "ggradar"
output:
  github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, dpi = 300, message = FALSE, warning = FALSE, error = FALSE)
```

This `ggradar` is modified from the [ggradar](https://github.com/ricardo-bion/ggradar), which allows you to build radar charts with multiple gridline.

## Install `ggradar`

```{r, eval=FALSE}
devtools::install_github("1156054203/ggradar", 
                          dependencies = TRUE)
```

## Use `ggradar`

```{r, fig.width=15, fig.height=10}
library(ggradar)
library(dplyr)
library(scales)
library(tibble)

set.seed(21)
sampleA <- sample(seq(1,23),size=23)
sampleB <- sample(seq(1,23),size=23)
data <- data.frame(group=c('sampleA','sampleB'),
                   t(data.frame(sampleA=sampleA,sampleB=sampleB)))
chroms <- paste0('chr',c(seq(1:22),'X'))
colnames(data)[-1] <- chroms
```

```{r, echo = FALSE}
knitr::kable(data[,1:10],format = "markdown")
```

```{r}
ggradar2(data,all.radar=seq(1:23),axis.label.size=3.5,grid.label.size=4,group.point.size=1,
         group.line.width=0.6, legend.position='right')
```

## Custom config

In addition to `all.radar` and `all.label`, other parameters are consistent with the original package [ggradar](https://github.com/ricardo-bion/ggradar).
Note:
`all.radar`: vector, each value is used to specify the gridline.
`all.label`: vector, each value is used to specify the label for gridline, default is value of `all.radar`.
`gridline.min.linetype`: used to specify gridline style.
`gridline.min.colour`: used to specify gridline colour.
